### 2019-10-25 paper/methods.tex
minor changes

As shown in Figure~\ref{fig:flow}, after launching the input file, we solve the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
routine provided by SERPENT-2 allows changes to the flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
Finally, we have to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. For non-thorium feed mechanism: mass of (HM) (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.

>>>>

As shown in Figure~\ref{fig:flow}, after launching the input file, we solve the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
routine provided by SERPENT-2 allows changes to the flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
Finally, we have to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. For non-thorium feed mechanism: mass of the heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.
